### 2016-01-20 Projects/DelCo_2012/Report/DelCo_2012.tex
Edit CAFS title

\headerB{
Examination of Compressed Air Foam (CAF) for Interior Firefighting \\
Spring 2012 \\
}

@@

Spray density experiments were conducted by placing 0.23~m$^2$ (2.5~ft$^2$) interlocking collector bins across the floor surface area of the burn rooms within each structure. The buildings were sheathed in plastic for the spray density tests to protect and preserve as much of the structure as possible before any fire suppression tests were conducted. Water flowed for a specified duration and upon completion the bins were removed from the structure. Each bin was then weighed to quantify the impact of nozzle location and spray pattern. Thirty-three spray density tests were conducted; 21 were in the burn building for the gas cooling tests and 12 were in the concrete structure for the suppression experiments. Tables\ref{tab:spray_density_tests} and \ref{tab:spray_density_tests2} provide an overview of each experiment. In the table, GC stands for the gas cooling experiments while SE stands for the suppression experiments. For all of the experiments, 100~ft (30~m) of 1~3/4~inch hoseline connected to a Blitz Fire monitor with a Metro 1 nozzle was used.

@@

\begin{table}[!ht]
\footnotesize
\centering
\captionof{table}{Spray Density Test Matrix for Gas Cooling Experiments}\label{tab:spray_density_tests}
\begin{tabular}{llllll}
\toprule[1.5pt]
Test \#    &   Flow Rate (gpm)  & Duration (s)  & Fluid  &  Pattern            & Nozzle Position  \\
\midrule
GC1        &   123              & 15            & Water  &  Solid Stream       & Back             \\
GC2        &   122              & 23            & Water  &  Solid Stream       & Back             \\
GC3        &   119              & 15            & Water  &  Solid Stream       & Mid              \\
GC4        &   118              & 15            & Water  &  Solid Stream       & Mid              \\
GC5        &   118              & 20            & Water  &  Solid Stream       & Mid              \\
GC6        &   120              & 21            & Water  &  30$^{\circ}$ Fog   & Mid              \\
GC7        &   118              & 20            & Water  &  30$^{\circ}$ Fog   & Mid              \\
GC8        &   119              & 22            & Water  &  30$^{\circ}$ Fog   & Back             \\
GC9        &   120              & 24            & Water  &  30$^{\circ}$ Fog   & Back             \\
GC10       &   127              & 20            & Water  &  Solid 7/8~in Slug  & Back             \\
GC11       &   120              & 22            & Water  &  Solid 7/8~in Slug  & Back             \\
GC12       &   120 / 60cfm      & 15            & CAF    &  Smooth Bore 7/8~in & Back             \\
GC13       &   120 / 60cfm      & 10            & CAF    &  Smooth Bore 7/8~in & Mid              \\
GC14       &   120 / 60cfm      & 15            & CAF    &  Smooth Bore 7/8~in & Back             \\
GC15       &   120 / 60cfm      & 20            & CAF    &  Smooth Bore 7/8~in & Mid              \\
GC16       &   120 / 60cfm      & 15            & CAF    &  30$^{\circ}$ Fog   & Mid              \\
GC17       &   120 / 60cfm      & 20            & CAF    &  Solid Stream       & Mid             \\
GC18       &   120 / 60cfm      & 10            & CAF    &  Solid Stream       & Mid             \\
GC19       &   120 / 60cfm      & 15            & CAF    &  30$^{\circ}$ Fog   & Back             \\
GC20       &   120 / 60cfm      & 15            & CAF    &  30$^{\circ}$ Fog   & Back             \\
GC21       &   120 / 60cfm      & 15            & CAF    &  Solid Stream       & Back             \\

@@

\begin{table}[!ht]
\footnotesize
\centering
\captionof{table}{Spray Density Test Matrix for Fire Suppression Experiments}\label{tab:spray_density_tests2}
\begin{tabular}{llllll}
\toprule[1.5pt]
Test \#    &   Flow Rate (gpm)  & Duration (s)  & Fluid  &  Pattern            & Nozzle Location  \\
\midrule
SE1        &   115              & 7             & Water  &  Solid Stream       &    Fire Room          \\
SE2        &   115              & 18            & Water  &  Solid Stream       &    Fire Room          \\
SE3        &   120              & 19            & Water  &  Solid Stream       &    Fire Room          \\
SE4        &   118              & 21            & Water  &  Solid Stream       &    Fire Room          \\
SE5        &   118              & 22            & Water  &  30$^{\circ}$ Fog   &    Fire Room          \\
SE6        &   118              & 19            & Water  &  30$^{\circ}$ Fog   &    Fire Room          \\
SE7        &   125              & 16            & Water  &  Solid 7/8~in Slug  &    Fire Room          \\
SE8        &   120              & 17            & Water  &  Solid 7/8~in Slug  &    Hallway            \\
SE9        &   116              & 15            & Water  &  30$^{\circ}$ Fog   &    Hallway            \\
SE10       &   116              & 16            & Water  &  30$^{\circ}$ Fog   &    Hallway            \\
SE11       &   116              & 16            & Water  &  Solid Stream       &    Hallway            \\
SE12       &   117              & 16            & Water  &  Solid Stream       &    Hallway            \\
\bottomrule[1.25pt]
\end{tabular}\par
\end{table}

>>>>

\headerB{
Examination of Compressed Air Foam (CAF) for Interior Firefighting \\
}

@@

Spray density experiments were conducted by placing 0.23~m$^2$ (2.5~ft$^2$) interlocking collector bins across the floor surface area of the burn rooms within each structure. The buildings were sheathed in plastic for the spray density tests to protect and preserve as much of the structure as possible before any fire suppression tests were conducted. Water flowed for a specified duration and upon completion the bins were removed from the structure. Each bin was then weighed to quantify the impact of nozzle location and spray pattern. Thirty-three spray density tests were conducted; 21 were in the burn building for the gas cooling tests and 12 were in the concrete structure for the suppression experiments. The flow rate for each test was 120~gpm for water and 120~gpm plus 60~cfm for CAFS. Tables\ref{tab:spray_density_tests} and \ref{tab:spray_density_tests2} provide an overview of each experiment. In the table, GC stands for the gas cooling experiments while SE stands for the suppression experiments. For all of the experiments, 100~ft (30~m) of 1~3/4~inch hoseline connected to a Blitz Fire monitor with a Metro 1 nozzle was used.

@@

\begin{table}[!ht]
\footnotesize
\centering
\captionof{table}{Spray Density Test Matrix for Gas Cooling Experiments}\label{tab:spray_density_tests}
\begin{tabular}{lllll}
\toprule[1.5pt]
Test \#    &  Duration (s)  & Agent  &  Pattern            & Nozzle Position  \\
\midrule
GC1        &  15            & Water  &  Solid Stream       & Back             \\
GC2        &  23            & Water  &  Solid Stream       & Back             \\
GC3        &  15            & Water  &  Solid Stream       & Mid              \\
GC4        &  15            & Water  &  Solid Stream       & Mid              \\
GC5        &  20            & Water  &  Solid Stream       & Mid              \\
GC6        &  21            & Water  &  30$^{\circ}$ Fog   & Mid              \\
GC7        &  20            & Water  &  30$^{\circ}$ Fog   & Mid              \\
GC8        &  22            & Water  &  30$^{\circ}$ Fog   & Back             \\
GC9        &  24            & Water  &  30$^{\circ}$ Fog   & Back             \\
GC10       &  20            & Water  &  Solid 7/8~in Slug  & Back             \\
GC11       &  22            & Water  &  Solid 7/8~in Slug  & Back             \\
GC12       &  15            & CAF    &  Smooth Bore 7/8~in & Back             \\
GC13       &  10            & CAF    &  Smooth Bore 7/8~in & Mid              \\
GC14       &  15            & CAF    &  Smooth Bore 7/8~in & Back             \\
GC15       &  20            & CAF    &  Smooth Bore 7/8~in & Mid              \\
GC16       &  15            & CAF    &  30$^{\circ}$ Fog   & Mid              \\
GC17       &  20            & CAF    &  Solid Stream       & Mid             \\
GC18       &  10            & CAF    &  Solid Stream       & Mid             \\
GC19       &  15            & CAF    &  30$^{\circ}$ Fog   & Back             \\
GC20       &  15            & CAF    &  30$^{\circ}$ Fog   & Back             \\
GC21       &  15            & CAF    &  Solid Stream       & Back             \\

@@

\begin{table}[!ht]
\footnotesize
\centering
\captionof{table}{Spray Density Test Matrix for Fire Suppression Experiments}\label{tab:spray_density_tests2}
\begin{tabular}{lllll}
\toprule[1.5pt]
Test \#    & Duration (s)  & Agent  &  Pattern            & Nozzle Location  \\
\midrule
SE1        & 7             & Water  &  Solid Stream       &    Fire Room          \\
SE2        & 18            & Water  &  Solid Stream       &    Fire Room          \\
SE3        & 19            & Water  &  Solid Stream       &    Fire Room          \\
SE4        & 21            & Water  &  Solid Stream       &    Fire Room          \\
SE5        & 22            & Water  &  30$^{\circ}$ Fog   &    Fire Room          \\
SE6        & 19            & Water  &  30$^{\circ}$ Fog   &    Fire Room          \\
SE7        & 16            & Water  &  Solid 7/8~in Slug  &    Fire Room          \\
SE8        & 17            & Water  &  Solid 7/8~in Slug  &    Hallway            \\
SE9        & 15            & Water  &  30$^{\circ}$ Fog   &    Hallway            \\
SE10       & 16            & Water  &  30$^{\circ}$ Fog   &    Hallway            \\
SE11       & 16            & Water  &  Solid Stream       &    Hallway            \\
SE12       & 16            & Water  &  Solid Stream       &    Hallway            \\
\bottomrule[1.25pt]
\end{tabular}\par
\end{table}
